Attempting to pull iterations out of RSiena

### 2017-01-25 iterationsfromRSiena.Rmd
more nightmarish unpacking

>>>>

Plots of the attribute data:

```{r plotsattr}
ggplot(ansnullattrs) + 
  geom_histogram(aes(x = mu), binwidth = .25)
ggplot(ansnullattrs) + 
  geom_histogram(aes(x = sigma2))
ggplot(ansnullattrs) + 
  geom_point(aes(x= mu, y = sigma2))
cor(ansnullattrs$mu, ansnullattrs$sigma2)
```

Okay, `mu` and `sigma2` are perfectly correlated. Does this make sense??? Are they monotonic maybe? Check:

```{r plotattrs2}
ggplot(ansnullattrs) + 
  geom_line(aes(x= rep, y = mu, color = as.factor(period)))
ggplot(ansnullattrs) + 
  geom_line(aes(x= rep, y = mu)) + 
  facet_wrap(~period, nrow = 2, labeller = "label_both")
```

Okay, couple things:

1. period 2 values of `mu` are pretty consistently lower than period 1 values of `mu`
2. they're definitely no monotonic with rep, and they look like typical chains from an MCMC.

I assume the `sigma2` plots have the same appearance since `mu` and `sigma` are perfectly correlated.
